Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-18 analysis/paper/paper.Rmd
Update to results, added code for primrary component composition and a few extra comments

```
<!-- QH: Later on, the language "the visualization above" will be changed to "Figure X." -->

@@

  It should also be noted that shape variation is not equal along both primary dimensions. For flakes in all three dorsal cortex classes, the largest differences between each inter-nested is along the first primary dimension. Slight differences are seen along the second primary dimension, with an increasing amount of variation as one goes from primary to secondary to tertiary flakes, but these changes are minor when compared to the larger changes seen in the first primary dimension. 
# Discussion

>>>>

```
<!-- QH: Later on, the language "the visualization above" will be changed to "Figure X." -->
<!-- QH: Also, on a secondary note, I had to copy the data file into a different location. That means that there are redundant data files that will need to be cleaned up later -->

@@

  It should also be noted that shape variation is not equal along both primary dimensions. For flakes in all three dorsal cortex classes, the largest differences between each inter-nested is along the first primary dimension. Slight differences are seen along the second primary dimension, with an increasing amount of variation as one goes from primary to secondary to tertiary flakes, but these changes are minor when compared to the larger changes seen in the first primary dimension.

<!-- QH: This code chunk below I copied from the old repo. The visualizations on dimension contributions are relevant to my second paragraph. I need to go back to some of my old work to see which values pertain to which measurement on the flakes, and to write up a paragraph or two elaborating on what I have already said. -->

```{r}
# let's look at all the PCs and how much each original # variable contributes to them

#view how much variation is described by each PC (ordered from PC1 to last PC)
enframe(100*pca.geo$sdev^2/sum(pca.geo$sdev^2))

#get meaningful PCs
getMeaningfulPCs(pca.geo$sdev^2, n = length(lands_no_outliers_names))

#estimate contribution (%) of landmarks on PC1
PC1_contrib <- fviz_contrib(pca.geo, choice = "var", axes = 1)
# take a look at the plot
PC1_contrib

LM_contrib_PC1 <- data.frame(LM = rep(NA, nrow(PC1_contrib$data)/2),
                             PC1_contrib = rep(NA, nrow(PC1_contrib$data)/2))
for (i in 1:(nrow(PC1_contrib$data)/2)) {
  LM_contrib_PC1$PC1_contrib[i] <- sum(PC1_contrib$data[(i*2-1):(i*2),]$contrib)
  LM_contrib_PC1$LM[i] <- as.character(i)
}

# TODO: decode the x-axis labels on the scree plot so we can describe in
# terms of actual flake dimension, write some sentences to describe and interpret

# estimate contribution (%) of landmarks on PC2
PC2_contrib <- fviz_contrib(pca.geo, choice = "var", axes = 2)
# take a look at the plot
PC2_contrib

LM_contrib_PC2 <- data.frame(LM = rep(NA, nrow(PC2_contrib$data)/2),
                             PC2_contrib = rep(NA, nrow(PC2_contrib$data)/2))
for (i in 1:(nrow(PC2_contrib$data)/2)) {
  LM_contrib_PC2$PC2_contrib[i] <- sum(PC2_contrib$data[(i*2-1):(i*2),]$contrib)
  LM_contrib_PC2$LM[i] <- as.character(i)
}

# examine landmarks with major contribution (%) to PC1 and PC2
important_LMs_PC1 <- LM_contrib_PC1[LM_contrib_PC1$PC1_contrib > 100/(nrow(PC1_contrib$data)/2),]
important_LMs_PC1[order(decreasing = T, important_LMs_PC1$PC1_contrib),]
important_LMs_PC2 <- LM_contrib_PC2[LM_contrib_PC2$PC2_contrib > 100/(nrow(PC2_contrib$data)/2),]
# here is a table that summarises the most important landmarks in the PCA
important_LMs_PC2[order(decreasing = T, important_LMs_PC2$PC2_contrib),]

# Discussion
